Test Suite Parallelization in Open-Source Projects:\\ A Study on Its Usage and Impact

### 2019-06-28 tse19/main.tex
updates

\begin{table}[t!]
\centering
\caption{
\label{tab:speedup}
Speedup (or slowdown) of parallel execution ($T_p$)
over sequential execution ($T_s$).  Default parallel configuration of
Maven is used.  Highest slowdown/speedup appears in gray color.}
\resizebox{.41\textwidth}{!}{%
%  \scriptsize
\begin{tabular}{llrrr}
\toprule
\emph{Group} & \emph{Subject} & \multicolumn{1}{c}{$T_s$} & \multicolumn{1}{c}{$T_p$} & $T_s/T_p$ \\%
\midrule%
Medium & Californium & 1.45m & 1.40m & \cellcolor{lightgray}1.04x\\%
Medium & \Comment{BounceStorage} Chaos\Comment{ HTTP Proxy} & 1.51m & 1.47m & \cellcolor{lightgray}1.03x\\%
Medium &\Comment{ Apache }Flink& 11.79m & 2.57m & 4.59x\\%
Long &\Comment{ Apache }Log4J2& 8.24m & 8.21m & \cellcolor{lightgray}1.00x\\%
Medium &Javaslang& 2.18m & 1.82m & 1.20x\\%
Medium &Jcabi\Comment{ GitHub} & 2.76m & 0.30m & 9.20x\\%
Long &\Comment{ Hazelcast }Jet& 8.26m & 3.67m & 2.25x\\%
Long & \Comment{apache} Mahout & 27.38m & 18.15m & 1.51x\\%
Long &\Comment{ Jankotek }MapDB& 10.06m & 8.58m & 1.17x\\%
Medium & \Comment{apache} OpenNLP & 1.30m & 0.55m & 2.36x\\%
Medium & \Comment{yegor256} Rultor & 2.30m & 0.27m & 8.52x\\%
Medium & \Comment{yegor256} Takes & 2.00m & 0.19m & \cellcolor{lightgray}10.53x\\%
Long & \Comment{vavr-io} Vavr & 3.26m & 2.25m & 1.45x\\%
\midrule
Average &  &  &  & \avgSpeedup{}x\\
\bottomrule%
\end{tabular}
}
\end{table}

>>>>

\begin{table}[t!]
\centering
\caption{
\label{tab:speedup}
Speedup (or slowdown) of parallel execution ($T_p$)
over sequential execution ($T_s$).  Default parallel configuration of
Maven is used.  Highest slowdown/speedup appears in gray color.}
\resizebox{.41\textwidth}{!}{%
%  \scriptsize
\begin{tabular}{llrrr}
\toprule
\emph{Group} & \emph{Subject} & \multicolumn{1}{c}{$T_s$} & \multicolumn{1}{c}{$T_p$} & $T_s/T_p$ \\%
\midrule%
Medium & \Comment{ Apache } Avro & 13.65m & 11.39m & \cellcolor{lightgray}1.20x\\%
Long & \Comment{ Apache } Oozie & 4.59m & 4.03m & \cellcolor{lightgray} 1.14x\\%
Medium & \Comment{ BounceStorage } Chaos & 1.54m & 1.44m & \cellcolor{lightgray} 1.07x\\%
Medium & \Comment{ Apache } OpenNLP & 3.59m & 2.36m & \cellcolor{lightgray} 1.52x\\%
%Long &\Comment{ Apache }Log4J2& 8.24m & 8.21m & \cellcolor{lightgray}1.00x\\%%
Medium & Cache2k & 1.56m & 1.47m & 1.06x\\%
Medium & Eclipse Leshan & 1.32m & 0.58m & 2.27x\\%
Long & Search Guard & 13.54m & 6.53m & 2.07x\\%
Long & Javaparser & 5.98m & 4.45m & 1.34x\\%
Long & Opta Planner & 12.55m & 10.07m & 1.25x\\%
Medium & Togglz & 4.01m & 3.65m & 1.10x\\%
Long & Twilio Java & 13.04m & 2.26m & 5.77x\\%
Medium & Vavr & 5.21m & 4.37m & \cellcolor{lightgray}1.26x\\%
Medium & Zxing & 1.33m & 2.61m & 1.26x\\%
\midrule
Average &  &  &  & \avgSpeedup{}x\\
\bottomrule%
\end{tabular}
}
\end{table}
